Document as a Data

### 2020-11-12 xaringan-OCR.Rmd
embeded xaringan OCR slideshow

class: middle

@@

.footnote[
Kathy Haramundanis and Larry Rowland (Hewlett-Packard Company), "Experience paper: a content reuse documentation design experience", SIGDOC '07 Proceedings of the 25th annual ACM international conference on Design of communication Pages 229-233, El Paso, Texas, USA — October 22 - 24, 2007
]

>>>>

@@

.footnote[
Kathy Haramundanis and Larry Rowland (Hewlett-Packard Company), "Experience paper: a content reuse documentation design experience", SIGDOC '07 Proceedings of the 25th annual ACM international conference on Design of communication Pages 229-233, El Paso, Texas, USA — October 22 - 24, 2007
]
]
